### 2011-01-26 paper/learningMethods.tex
added vector equation

\begin{verbatim}
        [g_0(t) ]    [ \amp * sin(\tau t) ]
        [g_1(t) ]    [ \amp * sin(\tau t) ]
        [g_2(t) ]    [ \amp * sin(\tau t) ]
g(t)   [g_3(t) ] = [ \amp * sin(\tau t) ]
        [g_4(t) ]    [ \amp * sin(\tau t) ]
        [g_5(t) ]    [ \amp * sin(\tau t) ]
        [g_6(t..) ]    [ \amp * sin(\tau t) ]
\end{verbatim}

>>>>

\[
\vec{g}(t) =
\left[ {\begin{array}{cc} 
a \cdot \sin(\frac{2\pi t}{\tau}) \cdot m_F \cdot m_O & + offset \\ % 0
a \cdot \sin(\frac{2\pi t}{\tau}) \cdot m_F           & + offset \\ % 1
a \cdot \sin(\frac{2\pi t}{\tau})                     & + offset \\ % 2
a \cdot \sin(\frac{2\pi t}{\tau}) \cdot m_O           & + offset \\ % 3
a \cdot \sin(\frac{2\pi t}{\tau}) \cdot m_R           & + offset \\ % 4
a \cdot \sin(\frac{2\pi t}{\tau}) \cdot m_R \cdot m_O & + offset \\ % 5
a \cdot \sin(\frac{2\pi t}{\tau}) \cdot m_F \cdot m_R & + offset \\ % 6
a \cdot \sin(\frac{2\pi t}{\tau}) \cdot m_F \cdot m_R & + offset \\ % 7
0                                                     & + offset \\ % 8
\end{array} } \right]
\]
